On the Use of K-Competitive Networks \\ for Writing Style Transfer

### 2017-12-02 dl_style_transfer/paper/main.tex
Updated paper

In this paper, we explore the use of $k$-competitive convolutional layers, a generalization of $k$-competitive layers designed for autoencoders in \cite{KATE}, which in turn are based on $k$-sparse layers as defined in \cite{MakhzaniF13}. These layers are integrated into a word-level convolutional neural network \cite{Kim14f}, and we perform a qualitative analysis on the quality of content and style representations generated by these networks.

% RELATED WORK
\section{Related Work}

% PRELIMINARY ANALYSIS
\section{Preliminary Analysis}
The majority of implementations of style transfer for images use the VGG-19 \cite{VGG19} architecture to generate content and style representations of an image. This network was trained to classify between 1000 images of the ImageNet challenge dataset \cite{ILSVRC15} and therefore is able to generate informative feature representations of a very large variety of objects. Given the resources required to train a similarly robust classifier for text, we first explore the tradeoffs of using an underlying network that is trained to discriminate between a much smaller number of classes by training a VGG network with the CIFAR-10 dataset \cite{Krizhevsky09} (here, we use pre-trained weights provided by \cite{Liu15}). Although this modified network is far less generalizable in terms of classification, we found that the content representations provided by later layers of the network were still informative enough to reconstruct the original image, even for images containing objects not included in the 10 classes of CIFAR-10.

@@

As the baseline for our comparisons we use a word-level convolutional neural network as designed by Yoon Kim in \cite{Kim14f}.

>>>>

In this paper, we explore the use of $k$-competitive convolutional layers, a generalization of $k$-competitive layers designed for autoencoders in \cite{KATE}, which in turn are based on $k$-sparse layers as defined in \cite{MakhzaniF13}. These layers are integrated into a word-level convolutional neural network \cite{Kim14f}, and we perform a qualitative analysis of the quality of content and style representations generated by these networks. A key benefit of our method is that it does not require a training set of translations between writing styles, which are very difficult to obtain.

% RELATED WORK
\section{Related Work}
Early methods at quantitatively determining the writing style of a piece of text focused on statistical analyses of the rates of passive and active sentences, the ratio of pronouns to nouns to adjectives, and the likelihood of adjacent words given their distribution in the English language. However, these methods rely on unreliable tokenizations and are difficult to adapt to style transfer. Xu et. al. \cite{Xu12} provided some of the first algorithmic style transfer methods between Shakespearean and modern English, but relied on a phrase table and did not take advantage of modern machine learning methods.

Recent methods based on neural networks fall into two broad categories: those that treat the problem as a mono-linguistic machine translation problem, and those that attempt to generate style and content representations of text.  \cite{Carlson17} and \cite{Jang16} fall under this first category, and generate stylized text that perform well according to BLEU score \cite{Papineni02}. However, these translation-based methods require a large dataset of tupled phrases that are identical in content and differ only in style. Use of passages in the Bible in \cite{Carlson17} and SparkNotes' Shakespearean translations in \cite{Jang16} present interesting but impractical test cases, while generating rap lyric translations with Google Translate via French \cite{Jang16} leaves much to be desired in terms of accuracy.

\cite{Edirisooriya} and \cite{Kabbara16} both consider a similar method to ours in terms of generating style and content representations of text, and \cite{Kabbara16} defines three evaluation criteria: soundness (preservation of content), coherence (grammatical correctness \& common sense), and effectiveness (matches intended style). However, these lack sufficient experiments with which to evaluate the quality of their results.

% PRELIMINARY ANALYSIS
\section{Preliminary Analysis}
The majority of implementations of style transfer for images use the VGG-19 \cite{VGG19} architecture to generate content and style representations of an image. This network was trained to classify images into one of the one thousand classes of the ImageNet challenge dataset \cite{ILSVRC15} and therefore is able to generate informative feature representations of a very large variety of objects. Given the resources required to train a similarly robust classifier for text, we first explore the tradeoffs of using an underlying network that is trained to discriminate between a much smaller number of classes by training a VGG network with the CIFAR-10 dataset \cite{Krizhevsky09} (here, we use pre-trained weights provided by \cite{Liu15}). Although this modified network is far less generalizable in terms of classification, we found that the content representations provided by later layers of the network were still informative enough to reconstruct the original image, even for images containing objects not included in the 10 classes of CIFAR-10.

@@

As the baseline for our comparisons we use a word-level convolutional neural network as designed by Yoon Kim in \cite{Kim14f}. A 1-d convolutional layer varies from those commonly found in architectures for image classification in that the receptive field of a filter is one-dimensional, and subsequent pooling layers operate along the time axis. The network takes as input a sentence, with each word encoded as a vector. As a ``shallow'' architecture, the network performs layer of convolution with filter lengths of 3, 4, 5 with 100 feature maps each, before a max-over-time pooling operation and a softmax layer.
